\plaintitle

### 2017-03-31 chi/piecework/complexity.tex
keynote checkin

\subsubsection{\crowdworkpers}
\topic{Kittur et al. were among the first to ask
whether crowdsourcing could be used for more than parallelizing tasks~\cite{crowdForgeKittur}.}
Their work showed that it could, with proof--of--concept crowdsourcing of
encyclopedia articles and news summaries
--- tasks which could be verified or repeated
with reasonable expectations of similar results.
Seeking to raise the complexity ceiling,
researchers have since created
yet more applications and techniques,
including conversational assistants~\cite{lasecki2013chorus},
medical data interpreters~\cite{lasecki2013chorus}, and
idea generation~\cite{YuEncouragingOutside,yu2014distributed,Yu2016a}.

@@

\topic{It is now clear that this computational workflow approach works with some classes of complex tasks, but
the broader wicked problems largely remain unsolved.}
As a first example,
idea generation shows promise~\cite{YuEncouragingOutside,yu2014distributed,Yu2016a},
but there is as yet no general crowdsourced solution for
the broader goal of invention and innovation~\cite{fuge2014analysis}.
Second,
focused writing tasks are now feasible~\cite{Kim2017,bernsteinSoylent,Nebeling:2016:WCW:2858036.2858169,writingMicroTasks,agapie2015crowdsourcing}, but
there is no general solution to create
a cross--domain, high--quality crowd--powered author. 
Third,
data analysis tasks such as
clustering~\cite{chilton2013cascade},
categorization~\cite{andre2014crowd}, and
outlining~\cite{luther2015crowdlines}
are possible, but there is no general solution for sense--making.
It is not yet clear what insights would be required
to enable crowdsourced solutions for these broader wicked problems.

@@

\topic{Piecework's body of research most squarely addresses complexity in two of the cases we looked at earlier:
Airy's human computers and among industrial workers.}

@@

\topic{Moreover, piecework was limited to tasks that could be quickly and accurately evaluated.}

Hart argues that evaluation limited piecework's complexity:
at some point, evaluating multidimensional work for quality
(rather than for quantity) becomes infeasible.
In his words,
``if the quality of the output is more difficult to measure than the quantity [\ldots]
then a piecework system is likely to encourage
an over--emphasis on quantity~\dots~and an under--emphasis on quality''~\cite{hart2016rise}.
Complex work, which is often subjective to evaluate, falls victim to this pitfall.

>>>>

\subsubsection{\crowdworkpers}
\topic{Kittur et al. were among the first to ask whether crowdsourcing could be used for more than parallelizing tasks~\cite{crowdForgeKittur}.}
Their work showed that it could, with proof--of--concept crowdsourcing of
encyclopedia articles and news summaries
--- tasks which could be verified or repeated
with reasonable expectations of similar results.
Seeking to raise the complexity ceiling,
researchers have since created
yet more applications and techniques,
including conversational assistants~\cite{lasecki2013chorus},
medical data interpreters~\cite{lasecki2013chorus}, and
idea generation~\cite{Yu2016a,Yu2016b}.

@@

\topic{It is now clear that this computational workflow approach works with some classes of complex tasks, but the broader wicked problems largely remain unsolved.}
As a first example,
idea generation shows promise~\cite{Yu2016a,Yu2016b},
but there is as yet no general crowdsourced solution for
the broader goal of invention and innovation~\cite{fuge2014analysis}.
Second,
focused writing tasks are now feasible~\cite{Kim2017,bernsteinSoylent,Nebeling:2016:WCW:2858036.2858169,writingMicroTasks,agapie2015crowdsourcing}, but
there is no general solution to create
a cross--domain, high--quality crowd--powered author. 
Third,
data analysis tasks such as
clustering~\cite{chilton2013cascade},
categorization~\cite{andre2014crowd}, and
outlining~\cite{luther2015crowdlines}
are possible, but there is no general solution for sense--making.
It is not yet clear what insights would be required
to enable crowdsourced solutions for these broader wicked problems.

@@

Piecework's body of research most squarely addresses complexity in two of the cases we looked at earlier: Airy's human computers and among industrial workers.

@@

\topic{Moreover, piecework was limited to tasks that could be quickly and accurately evaluated.}
Hart argues that evaluation limited piecework's complexity:
at some point, evaluating multidimensional work for quality
(rather than for quantity) becomes infeasible.
In his words,
``if the quality of the output is more difficult to measure than the quantity [\ldots]
then a piecework system is likely to encourage
an over--emphasis on quantity~\dots~and an under--emphasis on quality''~\cite{hart2016rise}.
Complex work, which is often subjective to evaluate, falls victim to this pitfall.
